---
title: Use tabs to organize content
output: html_document
---

You can turn parallel sections to tabs in `html_document` output.
```{r echo=FALSE, message=FALSE, warning=FALSE}
library(kableExtra)
df_sp_hetero <- readRDS("model_outputs/df_sp_hetero.rds")
tables <- split( df_sp_hetero , f = df_sp_hetero$model )
```


## Results {.tabset}

### Plots

We show a scatter plot in this section.

```{r echo=FALSE}
kbl(tables[[1]]) %>%
  kable_minimal()
```

### Plots

We show a scatter plot in this section.

```{r echo=FALSE}
kbl(tables[[1]]) %>%
  kable_minimal()
```

### Plots

We show a scatter plot in this section.

```{r echo=FALSE}
kbl(tables[[1]]) %>%
  kable_minimal()
```
### Plots

We show a scatter plot in this section.

```{r echo=FALSE}
kbl(tables[[1]]) %>%
  kable_minimal()
```
### Plots

We show a scatter plot in this section.

```{r echo=FALSE}
kbl(tables[[1]]) %>%
  kable_minimal()
```
### Plots

We show a scatter plot in this section.

```{r echo=FALSE}
kbl(tables[[1]]) %>%
  kable_minimal()
```
### Plots

We show a scatter plot in this section.

```{r echo=FALSE}
kbl(tables[[1]]) %>%
  kable_minimal()
```
### Plots

We show a scatter plot in this section.

```{r echo=FALSE}
kbl(tables[[1]]) %>%
  kable_minimal()
```
### Plots

We show a scatter plot in this section.

```{r echo=FALSE}
kbl(tables[[1]]) %>%
  kable_minimal()
```
### Plots

We show a scatter plot in this section.

```{r echo=FALSE}
kbl(tables[[1]]) %>%
  kable_minimal()
```
### Plots

We show a scatter plot in this section.

```{r echo=FALSE}
kbl(tables[[1]]) %>%
  kable_minimal()
```
### Plots

We show a scatter plot in this section.

```{r echo=FALSE}
kbl(tables[[1]]) %>%
  kable_minimal()
```
### Plots

We show a scatter plot in this section.

```{r echo=FALSE}
kbl(tables[[1]]) %>%
  kable_minimal()
```
### Plots

We show a scatter plot in this section.

```{r echo=FALSE}
kbl(tables[[1]]) %>%
  kable_minimal()
```
### Plots

We show a scatter plot in this section.

```{r echo=FALSE}
kbl(tables[[1]]) %>%
  kable_minimal()
```
### Plots

We show a scatter plot in this section.

```{r echo=FALSE}
kbl(tables[[1]]) %>%
  kable_minimal()
```
### Plots

We show a scatter plot in this section.

```{r echo=FALSE}
kbl(tables[[1]]) %>%
  kable_minimal()
```
### Plots

We show a scatter plot in this section.

```{r echo=FALSE}
kbl(tables[[1]]) %>%
  kable_minimal()
```
### Plots

We show a scatter plot in this section.

```{r echo=FALSE}
kbl(tables[[1]]) %>%
  kable_minimal()
```
### Plots

We show a scatter plot in this section.

```{r echo=FALSE}
kbl(tables[[1]]) %>%
  kable_minimal()
```
### Plots

We show a scatter plot in this section.

```{r echo=FALSE}
kbl(tables[[1]]) %>%
  kable_minimal()
```
### Plots

We show a scatter plot in this section.

```{r echo=FALSE}
kbl(tables[[1]]) %>%
  kable_minimal()
```
### Plots

We show a scatter plot in this section.

```{r echo=FALSE}
kbl(tables[[1]]) %>%
  kable_minimal()
```
### Plots

We show a scatter plot in this section.

```{r echo=FALSE}
kbl(tables[[1]]) %>%
  kable_minimal()
```
### Plots

We show a scatter plot in this section.

```{r echo=FALSE}
kbl(tables[[1]]) %>%
  kable_minimal()
```
### Plots

We show a scatter plot in this section.

```{r echo=FALSE}
kbl(tables[[1]]) %>%
  kable_minimal()
```
### Plots

We show a scatter plot in this section.

```{r echo=FALSE}
kbl(tables[[1]]) %>%
  kable_minimal()
```
